---
title: "FlowState Report"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE, message=FALSE, echo=FALSE}
library(flexdashboard)
library(tidyverse)
library(plotly)
# Importing published ledger data
ledger = read.csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vRntCy1xwfHoiPlB1cCtokloUcuoJuRJgXP0dL9arQPorUe1kYs1cRms-k4x4S_CmJhPnFBMXYD5AWb/pub?output=csv")

# Importing published capital data
capital = read.csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vQreG9l9BQ3OwqNUXieLVD2MhhELChxrymJ9UkHQfyZHJM6h22VXlWYo0_CxPX2ncw9dh_GYlaYRY0m/pub?output=csv")

# Importing published magic operation data
magic.operation = read.csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vQSRMFF0TaPpLi9ruP1bBkZEeWVveMxzRhgvjrh3OuYe5CnrmMD3DCHOZM8cEPwhGsb4KLS_q1DPrSA/pub?output=csv")
```

# Financial

## Column 1 Charts

### Sales

```{r}
# Filtering for sales
sales = filter(ledger, Transaction == "Sales") %>%
  select(Timestamp, Value, Quantity, System) %>%
  mutate(Date = parse_date(as.character(Timestamp), "%m/%d/%Y %H:%M:%S"), .keep = "unused")

# Displaying bar graph of sales
ggplotly(
  ggplot(sales, aes(x = Date, y = Value, fill = System)) +
    geom_col(position = position_dodge(), show.legend = FALSE) +
    scale_fill_manual(values = c("BlueViolet", "LimeGreen")) +
    theme_minimal()
)
```

### Price/g

```{r}
# Filtering for prices per gram
prices = mutate(sales, Price = Value / Quantity) %>%
  select(Price, Date, System)

# Displaying line graph of prices per gram
ggplotly(
  ggplot(prices, aes(x = Date, y = Price, color = System)) +
    geom_line(show.legend = FALSE) +
    geom_point(show.legend = FALSE) +
    scale_color_manual(values = c("BlueViolet", "LimeGreen")) +
    theme_minimal()
)
```

## Column 2 Sales

### Balance

```{r}
# Calculating ledger balance
balance = sum(ledger$Value[which(ledger$Transaction == "Sales")]) - sum(ledger$Value[which(ledger$Transaction == "Purchase")])

# Displaying ledger balance
valueBox(balance, caption = "Balance", icon = "fa-balance-scale", color = ifelse(balance > 0, "SteelBlue", "Tomato"))
```

### Total Sales

```{r}
# Filtering for total sales
total.sales = filter(ledger, Transaction == "Sales") %>%
  select(Value) %>%
  summarize(sum(Value)) %>%
  as.numeric()

# Displaying total sales
valueBox(total.sales, caption = "Total Sales", icon = "fa-dollar-sign", color = "LightSlateGrey")
```

### Magic Sales

```{r}
# Filtering for magic sales
magic.sales = filter(ledger, Transaction == "Sales") %>%
  filter(System == "Magic") %>%
  select(Value) %>%
  summarize(sum(Value)) %>%
  as.numeric()

# Displaying magic sales
valueBox(magic.sales, caption = "Magic Sales", icon = "fa-dollar-sign", color = "BlueViolet")
```

### Average Price Magic

```{r}
# Calculating magic average price per gram
magic.price = filter(sales, System == "Magic") %>%
  transmute(Price = Value / Quantity) %>%
  summarize(mean(Price)) %>%
  as.numeric()

# Displaying magic average price per gram
valueBox(magic.price, caption = "Average Price Per Gram", icon = "fa-line-chart", color = "BlueViolet")
```

### Uncanni Sales

```{r}
# Filtering for uncanni sales
uncanni.sales = filter(ledger, Transaction == "Sales") %>%
  filter(System == "Uncanni") %>%
  select(Value) %>%
  summarize(sum(Value)) %>%
  as.numeric()

# Displaying uncanni sales
valueBox(uncanni.sales, caption = "Uncanni Sales", icon = "fa-dollar-sign", color = "LimeGreen")
```

### Average Price Uncanni

```{r}
# Calculating uncanni average price per gram
uncanni.price = filter(sales, System == "Uncanni") %>%
  transmute(Price = Value / Quantity) %>%
  summarize(mean(Price)) %>%
  as.numeric()

# Displaying uncanni average price per gram
valueBox(uncanni.price, caption = "Average Price Per Gram", icon = "fa-line-chart", color = "LimeGreen")
```

## Column 3 Capital

### Cole Capital Repayment

```{r}
# Filtering for cole investment
cole.inv = filter(capital, Partner == "Cole") %>%
  filter(Transaction == "Investment") %>%
  select(Amount) %>%
  summarize(sum(Amount)) %>%
  as.numeric()

# Filtering for cole repayment
cole.rep = filter(capital, Partner == "Cole") %>%
  filter(Transaction == "Repayment") %>%
  select(Amount) %>%
  summarize(sum(Amount)) %>%
  as.numeric()

# Displaying cole repayment gauge
gauge(cole.rep, 0, cole.inv,
      sectors = gaugeSectors(success = c(0.67*cole.inv, cole.inv),
                             warning = c(0.34*cole.inv, 0.66*cole.inv),
                             danger = c(0, 0.33*cole.inv),
                             colors = c("LimeGreen", "Coral", "Tomato")))
```

### Zac Capital Repayment

```{r}
# Filtering for zac investment
zac.inv = filter(capital, Partner == "Zac") %>%
  filter(Transaction == "Investment") %>%
  select(Amount) %>%
  summarize(sum(Amount)) %>%
  as.numeric()

# Filtering for zac repayment
zac.rep = filter(capital, Partner == "Zac") %>%
  filter(Transaction == "Repayment") %>%
  select(Amount) %>%
  summarize(sum(Amount)) %>%
  as.numeric()

# Displaying zac repayment gauge
gauge(zac.rep, 0, zac.inv,
      sectors = gaugeSectors(success = c(0.67*zac.inv, zac.inv),
                             warning = c(0.34*zac.inv, 0.66*zac.inv),
                             danger = c(0, 0.33*zac.inv),
                             colors = c("LimeGreen", "Coral", "Tomato")))
```

### Mike Capital Repayment

```{r}
# Filtering for mike investment
mike.inv = filter(capital, Partner == "Mike") %>%
  filter(Transaction == "Investment") %>%
  select(Amount) %>%
  summarize(sum(Amount)) %>%
  as.numeric()

# Filtering for mike repayment
mike.rep = filter(capital, Partner == "Mike") %>%
  filter(Transaction == "Repayment") %>%
  select(Amount) %>%
  summarize(sum(Amount)) %>%
  as.numeric()

# Displaying mike repayment gauge
gauge(mike.rep, 0, mike.inv,
      sectors = gaugeSectors(success = c(0.67*mike.inv, mike.inv),
                             warning = c(0.34*mike.inv, 0.66*mike.inv),
                             danger = c(0, 0.33*mike.inv),
                             colors = c("LimeGreen", "Coral", "Tomato")))
```

### Ryan Capital Repaymet

```{r}
# Filtering for ryan investment
ryan.inv.magic = filter(capital, Partner == "Ryan") %>%
  filter(Transaction == "Investment") %>%
  select(Amount) %>%
  summarize(sum(Amount)) %>%
  as.numeric()

ryan.inv.uncanni = filter(ledger, System == "Uncanni") %>%
  filter(Transaction == "Purchase") %>%
  select(Value) %>%
  summarize(sum(Value)) %>%
  as.numeric()

ryan.inv = ryan.inv.magic + ryan.inv.uncanni

# Filtering for ryan repayment
ryan.rep = filter(capital, Partner == "Ryan") %>%
  filter(Transaction == "Repayment") %>%
  select(Amount) %>%
  summarize(sum(Amount)) %>%
  as.numeric()

# Displaying ryan repayment gauge
gauge(ryan.rep, 0, ryan.inv,
      sectors = gaugeSectors(success = c(0.67*ryan.inv, ryan.inv),
                             warning = c(0.34*ryan.inv, 0.66*ryan.inv),
                             danger = c(0, 0.33*ryan.inv),
                             colors = c("LimeGreen", "Coral", "Tomato")))
```

# Operations

## Column 1 Charts

### Yields

```{r}
# Filtering for yield
yield = select(magic.operation, Timestamp, Yield) %>%
  mutate(Date = parse_date(as.character(Timestamp), "%m/%d/%Y %H:%M:%S"), .keep = "unused") %>%
  group_by(Date) %>%
  summarize(Yield = sum(Yield))

# Displaying bar graph of yield
ggplotly(
  ggplot(yield, aes(x = Date, y = Yield)) +
    geom_col(fill = "BlueViolet") +
    theme_minimal()
)
```

### Contaminations

```{r}
# Filtering for contaminations
contams = select(magic.operation, Timestamp, Operation, Contaminates, Batch, Contaminations, Batch.1, Contaminated) %>%
  mutate(Date = as.Date(Timestamp, "%m/%d/%y"), .keep = "unused") %>%
  unite(Contams, Contaminates, Contaminations, Contaminated, na.rm = TRUE)

# Displaying line graph of contaminations
ggplotly(
  ggplot(contams, aes(x = Date, y = Contams, col = Operation)) +
    geom_line(show.legend = FALSE) +
    geom_point(show.legend = FALSE) +
    scale_color_manual(values = c("DarkCyan", "DarkGrey", "DarkMagenta")) +
    theme_minimal()
)
```

## Column 2 Stats

### Stock

```{r}
# Filtering for total yield
total.yield = select(magic.operation, Yield) %>%
  summarise(sum(Yield, na.rm = TRUE)) %>%
  as.numeric()

# Filtering for quantity sold
total.sold = filter(ledger, Transaction == "Sales") %>%
  select(Quantity) %>%
  summarize(sum(Quantity, na.rm = TRUE)) %>%
  as.numeric()

# Calculating stock
stock = total.yield - total.sold

# Displaying current stock
valueBox(stock, caption = "Stock (g)", icon = "fa-briefcase", color = ifelse(stock > 0, "SteelBlue", "Tomato"))
```

### Average Weekly Yield

```{r}
# Filtering for weekly yield
weekly.yield = select(magic.operation, Timestamp, Yield) %>%
  mutate(Timestamp = parse_date(as.character(Timestamp), "%m/%d/%Y %H:%M:%S"), .keep = "unused") %>%
  mutate(Week = format(as.Date(Timestamp), "%W"), .keep = "unused") %>%
  group_by(Week) %>%
  summarize(sum(Yield, na.rm = TRUE))

# Calculating average weekly yield
average.weekly.yield = mean(weekly.yield[,2])

# Displaying average weekly yield
valueBox(average.weekly.yield, caption = "Average Weekly Yield (g)", icon = "fa-line-chart", color = "BlueViolet")
```

### Average Yield per Batch

```{r}

```

### Number of Dishes

```{r}
# Filtering for total dishes made
dishes.made = select(magic.operation, Copies) %>%
  summarize(sum(Copies, na.rm = TRUE)) %>%
  as.numeric()

# Filtering for total dishes used
dishes.used = select(magic.operation, Dishes) %>%
  summarize(sum(Dishes, na.rm = TRUE)) %>%
  as.numeric()

# Filtering for total dishes contaminated
dishes.contaminated = select(magic.operation, Contaminates) %>%
  summarize(sum(Contaminates, na.rm = TRUE)) %>%
  as.numeric()

# Calculating available dishes
dishes.available = dishes.made - dishes.used - dishes.contaminated

# Displaying available dishes
valueBox(dishes.available, caption = "Dishes Available", icon = "fa-circle-o", color = "DarkCyan")
```

### Number of Jars

```{r}
# Filtering for total jars made
jars.made = select(magic.operation, Jars) %>%
  summarize(sum(Jars, na.rm = TRUE)) %>%
  as.numeric()

# Filtering for total jars used
jars.used = select(magic.operation, Spawn) %>%
  summarize(sum(Spawn, na.rm = TRUE)) %>%
  as.numeric()

# Filtering for total jars contaminated
jars.contaminated = select(magic.operation, Contaminations) %>%
  summarize(sum(Contaminations)) %>%
  as.numeric()

# Calculating available jars
jars.available = jars.made - jars.used - jars.contaminated

# Displaying available jars
valueBox(jars.available, caption = "Jars in Incubation", icon = "fa-beer", color = "DarkGrey")
```

### Number of Tubs

```{r}
# Filtering for tubs spawned
tubs.spawned = select(magic.operation, Spawn) %>%
  filter(Spawn > 0) %>%
  as.data.frame() %>%
  nrow %>%
  as.numeric()

# Filtering for tubs harvested
tubs.harvested = select(magic.operation, Yield) %>%
  filter(Yield > 0) %>%
  as.data.frame() %>%
  nrow() %>%
  as.numeric()

# Calculating active tubs
tubs.active = tubs.spawned - tubs.harvested

# Displaying active tubs
valueBox(tubs.active, caption = "Tubs Active", icon = "fa-battery-empty", color = "DarkMagenta")
```

## Column 3 Targets
